Parallel Multipoint Approximation Method for Large Scale Optimization Problems \thanks{This study was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2017-11-23 2018/PAVT_Toropov/PAVT2018_MAM.tex
References updated

With $N=50$ segments (corresponding to 100 design variables) the SQP solution of this problem is $V = 63704.598\; cm^3$. The optimal values of design variables are given below (the first 50 entries are the widths and the last 50 entries are the heights of the segments):
\setcounter{MaxMatrixCols}{11}
\[
\begin{matrix}%[pos]{spalten}
			b=& 3.246& 3.224& 3.202& 3.179& 3.156& 3.133& 3.109& 3.085& 3.061& 3.036 \\  
			  & 3.011& 2.985& 2.959& 2.933& 2.905& 2.878& 2.850& 2.821& 2.792& 2.762 \\
			  & 2.731& 2.700& 2.668& 2.635& 2.602& 2.567& 2.532& 2.495& 2.458& 2.419 \\  
			  & 2.379& 2.338& 2.295& 2.250& 2.204& 2.156& 2.105& 2.052& 1.996& 1.936 \\  
			  & 1.873& 1.805& 1.732& 1.651& 1.562& 1.462& 1.345& 1.196& 1.023& 1.000 \\ 	
\end{matrix}
\]
\[
\begin{matrix}
	h=& 64.919&64.480&64.033&63.581&63.122&62.656&62.184&61.703&61.216&60.720  \\
		& 60.216&59.703&59.182&58.651&58.110&57.558&56.996&56.423&55.837&55.239  \\
		& 54.628&54.003&53.363&52.707&52.035&51.344&50.635&49.906&49.155&48.381  \\
		& 47.582&46.754&45.897&45.008&44.082&43.116&42.105&41.041&39.919&38.729  \\
		& 37.462&36.102&34.630&33.020&31.240&29.241&26.910&23.919&20.465&14.639  \\
\end{matrix}
\]

MAM obtained the solution $V = 63935.360\; cm^3$, using 1500 function evaluations (as compared to almost 8000 evaluations used by SQP). The number of points in a trust region used to build approximations was 150. The optimal values of design variables obtained by MAM are given below:
\[
\begin{matrix}
	b=&	3.238&3.204&3.202&3.170&3.176&3.128&3.108&3.089&3.057&3.003 \\  
		& 3.027&2.986&2.959&2.952&2.885&2.855&2.864&2.847&2.803&2.762 \\  
		& 2.737&2.722&2.630&2.645&2.590&2.558&2.547&2.480&2.693&2.391 \\ 
		& 2.368&2.310&2.307&2.227&2.176&2.149&2.106&2.016&2.007&1.925 \\  
		& 1.864&1.843&1.758&1.635&1.582&1.934&1.332&1.173&1.026&2.419 \\ 
\end{matrix}
\]
\[
\begin{matrix}
	h=& 64.764&64.083&64.036&63.392&63.518&62.566&62.153&61.772&61.149& 60.054  \\
		& 60.534&59.728&59.182&59.033&57.695&57.105&57.274&56.943&56.057&55.233  \\
		& 54.747&54.433&52.590&52.902&51.802&51.150&50.943&49.597&51.567&47.811  \\
		& 47.373&46.190&46.140&44.543&43.525&42.991&42.119&40.308&40.141&38.506  \\
		& 37.268&36.839&35.153&32.702&31.615&28.304&26.642&23.447&20.536& 9.417

\end{matrix}
\]

@@

\bibliography{bibliography}{}
\bibliographystyle{nature}

>>>>

With $N=50$ segments (corresponding to 100 design variables) the SQP solution of this problem is $V = 63704.598\; cm^3$. The optimal values of design variables are given below (the first 50 entries are the widths and the last 50 entries are the heights of the segments):
\setcounter{MaxMatrixCols}{11}
\[
\begin{matrix}%[pos]{spalten}
			b=& \left[3.246, \right.& 3.224,& 3.202,& 3.179,& 3.156,& 3.133,& 3.109,& 3.085,& 3.061,& 3.036,  \\  
			  & 3.011,& 2.985,& 2.959,& 2.933,& 2.905,& 2.878,& 2.850,& 2.821,& 2.792,& 2.762, \\
			  & 2.731,& 2.700,& 2.668,& 2.635,& 2.602,& 2.567,& 2.532,& 2.495,& 2.458,& 2.419, \\  
			  & 2.379,& 2.338,& 2.295,& 2.250,& 2.204,& 2.156,& 2.105,& 2.052,& 1.996,& 1.936, \\  
			  & 1.873,& 1.805,& 1.732,& 1.651,& 1.562,& 1.462,& 1.345,& 1.196,& 1.023,& \left. 1.000\right] 	
\end{matrix}
\]
\[
\begin{matrix}
	h=& \left[64.919,\right.&64.480,&64.033,&63.581,&63.122,&62.656,&62.184,&61.703,&61.216,&60.720  \\
		& 60.216,&59.703,&59.182,&58.651,&58.110,&57.558,&56.996,&56.423,&55.837,&55.239  \\
		& 54.628,&54.003,&53.363,&52.707,&52.035,&51.344,&50.635,&49.906,&49.155,&48.381  \\
		& 47.582,&46.754,&45.897,&45.008,&44.082,&43.116,&42.105,&41.041,&39.919,&38.729  \\
		& 37.462,&36.102,&34.630,&33.020,&31.240,&29.241,&26.910,&23.919,&20.465,&\left.14.639 \right]
\end{matrix}
\]

MAM obtained the solution $V = 63935.360\; cm^3$, using 1500 function evaluations (as compared to almost 8000 evaluations used by SQP). The number of points in a trust region used to build approximations was 150. The optimal values of design variables obtained by MAM are given below:
\[
\begin{matrix}
	b=&	\left[3.238,\right.&3.204,&3.202,&3.170,&3.176,&3.128,&3.108,&3.089,&3.057,&3.003 \\  
		& 3.027,&2.986,&2.959,&2.952,&2.885,&2.855,&2.864,&2.847,&2.803,&2.762 \\  
		& 2.737,&2.722,&2.630,&2.645,&2.590,&2.558,&2.547,&2.480,&2.693,&2.391 \\ 
		& 2.368,&2.310,&2.307,&2.227,&2.176,&2.149,&2.106,&2.016,&2.007,&1.925 \\  
		& 1.864,&1.843,&1.758,&1.635,&1.582,&1.934,&1.332,&1.173,&1.026,&\left.2.419\right]
\end{matrix}
\]
\[
\begin{matrix}
	h=& \left[64.764,\right.&64.083,&64.036,&63.392,&63.518,&62.566,&62.153,&61.772,&61.149,& 60.054  \\
		& 60.534,&59.728,&59.182,&59.033,&57.695,&57.105,&57.274,&56.943,&56.057,&55.233  \\
		& 54.747,&54.433,&52.590,&52.902,&51.802,&51.150,&50.943,&49.597,&51.567,&47.811  \\
		& 47.373,&46.190,&46.140,&44.543,&43.525,&42.991,&42.119,&40.308,&40.141,&38.506  \\
		& 37.268,&36.839,&35.153,&32.702,&31.615,&28.304,&26.642,&23.447,&20.536,& \left.9.417\right]
\end{matrix}
\]

@@

\begin{thebibliography}{10}

\bibitem{Toropov1989}
Toropov, V.:
\newblock Simulation approach to structural optimization.
\newblock Structural Optimization \textbf{1}, 37--46 (1989)

\bibitem{Toropov1992}
Toropov, V.:
\newblock Multipoint approximation method in optimization problems with expensive function values.
\newblock In: Sydow, A. (ed.) Proceedings of the 4th international symposium on Systems analysis and simulation, 
pp. 207--212, Elsevier,  (1992)

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using fem and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993)

\bibitem{ShahparPolynkinToropov2008}
Shahpar, S., Polynkin, A., Toropov, V.:
\newblock Large scale optimization of transonic axial compressor rotor blades.
\newblock In:  49th AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2008-2056
 (2008)

\bibitem{PolynkinToropovShahpar2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Design optimization of aircraft engine components.
\newblock In: Proc. of 7th ASMO UK / ISSMO Conf. on Engineering Design Optimization. Process and Product Improvement (2008)

\bibitem{PolynkinToropovShahpar2010}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Multidisciplinary optimization of turbomachinery based on metamodel built by genetic programming.
\newblock In: 13th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference (2010)

\bibitem{KeulenToropovMarkine1996}
van Keulen, F., Toropov, V., Markine, V.:
\newblock Recent refinements in the multi-point approximation method in conjunction with adaptive mesh refinement.
\newblock In: McCarthy, J.M. (ed.) Proc. of ASME Design Engineering Technical Conferences and Computers
  in Engineering Conf., 1--12, ASME, Irvine CA (1996)

\bibitem{ToropovKeulenMarkine1996}
Toropov, V., van Keulen, F., Markine, V., de~Boer, H.:
\newblock Refinements in the multi-point approximation method to reduce the effects of noisy responses.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization,  pp. 941--951, AIAA (1996)

\bibitem{ToropovMarkineHolden1999}
Toropov, V., Markine, V., Holden, C.:
\newblock Use of mid-range approximations for optimization problems with functions of domain-dependent calculability.
\newblock In: 3rd ISSMO/UBCAD/UB/AIAA World Congress of Structural and Multidisciplinary Optimization (1999).

\bibitem{ToropovMarkine1996}
Toropov, V., Markine, V.:
\newblock The use of simplified numerical models as mid-range approximations.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization, pp. 952--958 (1996).

\bibitem{ToropovAlvarez1998}
Toropov, V., Alvarez, L.:
\newblock Creation of multipoint approximations using genetic programming.
\newblock In: Parmee, I.C. (ed.) Adaptive Computing in Design and Manufacture, 3rd Int. Conf.,
   pp. 21--24, PEDC, Dartington (1998)

\bibitem{PolynkinToropov2012}
Polynkin, A. Toropov, V.:
\newblock Mid-range metamodel assembly building based on linear regression for large scale optimization problems.
\newblock Structural and Multidisciplinary Optimization \textbf{45}(4), 515--527 (2012)

\bibitem{LancasterSalkauskas1981}
Lancaster, P. Salkauskas, K.:
\newblock Surfaces generated by moving least squares methods.
\newblock Mathematics of Computation \textbf{87}, 141--158 (1981)

\bibitem{Liszka1984}
Liszka, T.:
\newblock An interpolation method for an irregular net of nodes.
\newblock Int. J. Num. Meth. \textbf{20}, 1599--1612 (1984)

\bibitem{ChoiYounYang2001}
Choi, K., Youn, B., Yang, R.-J.:
\newblock Moving least squares method for reliability-based design optimization.
\newblock In: 4th World Congress of Structural and Multidisciplinary Optimization, Dalian, China (2001)

\bibitem{ToropovSchrammSahaiJones2005}
Toropov, V., Schramm, U., Sahai, A., Jones, R., Zeguer, T.:
\newblock Design optimization and stochastic analysis based on the moving least squares method.
\newblock In: Herskovits, J., Mazorche, S., Canelas, A. (eds.) 6th World Congress of Structural and Multidisciplinary Optimization, art. no. 9412 (2005)

\bibitem{PolynkinToropov2010}
Polynkin, A. Toropov, V.:
\newblock Recognition of design variable inter-dependencies using  cross-validated moving least-squares method.
\newblock In: Proceedings of the 51st AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2010-2985 (2010)

\bibitem{OllarToropovJones2014}
Ollar, J., Toropov, V., Jones. R.:
\newblock  Mid-range approximations in sub-spaces for MDO problems with disparate discipline attributes.
\newblock In: 15th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2014-2437 (2014)

\bibitem{KeulenToropov1997}
van Keulen, F. Toropov, V.:
\newblock New developments in structural optimization using adaptive mesh refinement and multi-point approximations.
\newblock Engineering Optimization \textbf{29}, 217--234 (1997)

\bibitem{PolynkinToropov2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Adaptive and parallel capabilities in the multipoint approximation  method.
\newblock In: 12th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2008-5803 (2008)

\bibitem{Vanderpllaats2001}
Vanderplaats, G.:
\newblock Multidiscipline Design Optimization. 
\newblock Vanderplaats Research \& Development, Inc., Colorado Springs, (2001)

\end{thebibliography}
